---
title: "Eating Out"
author: "Cleo Ware"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "Fall 2023"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## There were two years in which the General Social Survey asked about the frequency of eating out. The variable name you are looking for is "eatout".
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE, warning=FALSE}
GSS <- readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

#introduction

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


#methods 
After looking at the data, We will use the CandP helper files to compare categories~categories. This will also include tidyverse for percentages and ggplots2. Then we will look at the data.

# Results



## Graphificial results

```{r}
barchartGC(~race + eatout,data=mydata, type="percent")
```

Data shows "white" race is eating out more overall then "other" and "black" races

## Numerical Results

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
```

The data again shows that the "white"races outs out more (almost 20%) then "other"
and "black" races.

## Inferential Results

```{r}
chisqtestGC(table1)
```

The results from the chi-square test show that whites have that "whites" indeed eatout at a higher rate then any other race.

```{r}
fisher.test(table1)
```

## Conclusion and Discussion 

After using CandP helper file Cat~Cat to run Barchart, table1, chi-square and
fisher test, the results of all test confirmed that the "white" race eatout more
than the "other" race and "black". In fact, the "white" race was more than 20% more likely to eat out than any of the other races. (other or black).

Thus, we must reject the $H_0$ that There is no difference among the various races with frequency of eating out. 
